---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "ben kimel green"
date: "2/27/2019"
output: 
  html_document: 
    theme: yeti
    toc: yes
    toc_depth: 2
---
# Midterms
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
## The tidyverse packages

#### 1. Can you name which package is associated with each task below?
  + Plotting - ggplot2
  + Data munging/wrangling - dplyr
  + Reshaping (speading and gathering) data - tidyr
  + Importing/exporting data - readr
  
#### 2. Now can you name two functions that you’ve used from each package that you listed above for these tasks?

  + ggplot2 - ggplot, geom_point
  + dplyr - filter, summarise
  + tidyr - spread, separate
  + readr - read_csv, write_delim

##R Basics 

#### 1. Fix this code with the fewest number of changes possible so it works:

```{r}
My_data.name___is.too00ooLong <- c( 1 , 2   , 3 )
```

#### 2. Fix this code so it works:

```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')
```

#### 3. Look at the code below and comment on what happened to the values in the vector.
The vector changed all the values to be of type char

```{r}
my_vector <- c(1, 2, '3', '4', 5)
my_vector
```

## Data import/export

#### 1. Download the rail_trail.txt file from Canvas (in the Midterm Exam section) and successfully import it into R. Prove that it was imported successfully by including your import code and taking a glimpse of the result.
```{r}
file_path <- '~/Desktop/rail_trail.txt'
trails <- read_delim(file = file_path,delim = "|")
glimpse(trails)
```

#### 2. Export the file into a comma-separated file and name it “rail_trail.csv”. Make sure you define the path correctly so that you know where it gets saved. Then reload the file. Include your export and import code and take another glimpse.
```{r}
file_path_write <- '~/Desktop/rail_trail.csv'
write_csv(trails,file_path_write)
trails_csv <- read_csv(file = file_path_write)
glimpse(trails_csv)
```
##Visualization

#### 1.Critique this graphic: give only three examples of what is wrong with this graphic. Be concise.

1. Combining age related description together with gender. I would use 2 diffrent graphics.
2. Using a sized circle to show propetion from is confusing. Bar chart or even pie chart would have been nicer. 
3. The numbers don't add up to 100% and the 10%-5%  missing are not explained

#### 2. Reproduce this graphic using the `diamonds` data set.
```{r}
data(diamonds)
ggplot(data = diamonds) +
  geom_boxplot(mapping = aes(x = cut, y = carat, fill = color),position = "identity")+
  scale_fill_brewer(palette="Set2")+
  labs(x = "CUT OF DIAMONDS", y = "CARAT OF DIAMOND")+
  coord_flip()
```

##Data munging and wrangling

#### 1. Is this data “tidy”? If yes, leave it alone and go to the next problem. If no, make it tidy. Note: this data set is called table2 and is available in the tidyverse package. It should be ready for you to use after you’ve loaded the tidyverse package.

#### 2. Create a new column in the diamonds data set called price_per_carat that shows the price of each diamond per carat (hint: divide). Only show me the code, not the output.

#### 3. For each cut of diamond in the diamonds data set, how many diamonds, and what proportion, have a price > 10000 and a carat < 1.5? There are several ways to get to an answer, but your solution must use the data wrangling verbs from the tidyverse in order to get credit.

+ Do the results make sense? Why?
+ Do we need to be wary of any of these numbers? Why?
