---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "ben kimel green"
date: "2/27/2019"
output: 
  html_document: 
    theme: yeti
    toc: yes
    toc_depth: 4
---
# Midterms
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
## The tidyverse packages

#### 1. Can you name which package is associated with each task below?
  + Plotting - ggplot2
  + Data munging/wrangling - dplyr
  + Reshaping (speading and gathering) data - tidyr
  + Importing/exporting data - readr
  
#### 2. Now can you name two functions that you’ve used from each package that you listed above for these tasks?

  + ggplot2 - ggplot, geom_point
  + dplyr - filter, summarise
  + tidyr - spread, separate
  + readr - read_csv, write_delim

##R Basics 

#### 1. Fix this code with the fewest number of changes possible so it works:

```{r}
My_data.name___is.too00ooLong <- c( 1 , 2   , 3 )
```

#### 2. Fix this code so it works:

```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')
```

#### 3. Look at the code below and comment on what happened to the values in the vector.
The vector changed all the values to be of type char

```{r}
my_vector <- c(1, 2, '3', '4', 5)
my_vector
```

## Data import/export

#### 1. Download the rail_trail.txt file from Canvas (in the Midterm Exam section) and successfully import it into R. Prove that it was imported successfully by including your import code and taking a glimpse of the result.
```{r}
file_path <- '~/Desktop/rail_trail.txt'
trails <- read_delim(file = file_path,delim = "|")
glimpse(trails)
```

#### 2. Export the file into a comma-separated file and name it “rail_trail.csv”. Make sure you define the path correctly so that you know where it gets saved. Then reload the file. Include your export and import code and take another glimpse.
```{r}
file_path_write <- '~/Desktop/rail_trail.csv'
write_csv(trails,file_path_write)
trails_csv <- read_csv(file = file_path_write)
glimpse(trails_csv)
```
##Visualization

#### 1.Critique this graphic: give only three examples of what is wrong with this graphic. Be concise.

1. it's bad
2. it's bad
3. it's not good