---
title: "COMPSCIX 415.2 Homework 1"
author: "ben kimel green"
date: "1/29/2019"
#output: pdf_document

---
```{r load_packages, warning=FALSE, message=FALSE}
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(mdsr)
library(tidyverse)
data("WorldCities")

```
World cities
---
There are 10 variables in the World Cities dataset. Among them one can find city name,country and population, Geographic variables and other important variables such as code, and date (estimated data collection date)
```{r}
glimpse(WorldCities)
WorldCities <- head(WorldCities, 200) 
```
```{r}
country_col <- WorldCities$country
unique(country_col)
```
QUESTION 2: There is a column called region in the data set. Can you extract this and show
only the unique values? 
```{r}
region_col <- WorldCities$region
unique(region_col)
```

```{r}
#same with function or verb
country_col <- select(WorldCities, country)
#same with a pipe
country_col <- WorldCities %>% select(country)
#chainig pipes
WorldCities %>% select(region) %>% head(5)
```
QUESTION 3: Can you extract and show the unique entries from the country column in
WorldCities using one line of code and two %>% operators? 
```{r}
WorldCities%>%select(country)%>%unique()
```
Visualisation
```{r}
WorldCities %>% ggplot(aes(x = population)) +
geom_histogram() +
xlab('City Population')
```
QUESTION 4: Make one more histogram of the population and add a new x-label, a new ylabel, a new title (use ggtitle('my title')), and change the theme of the plot using theme_bw().
```{r}
WorldCities %>% ggplot(aes(x = population)) +
geom_histogram() +
xlab('Population of the city!') +
ylab('Headcount') +
ggtitle('Best Histogram') +
theme_bw()
```