---
title: "COMPSCIX 415.2 Homework 9/Final"
author: "ben kimel green"
date: "3/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
```

###STEP 1

Write an R function that does the following:

* Takes a sample of size samp_size from this exponential distribution (samp_size is an input parameter for the function)
* Calculates the mean of that sample
* Calculates the standard deviation of that sample
* Returns the calculated mean and standard deviation as a list
```{r}
samp_fun <- function(samp_size, samp_rate) {
  
  sample <- rexp(n = samp_size, rate = samp_rate)
  samp_avg <- mean(sample)
  samp_std_dev <-sd(sample)
  stats <- list(samp_avg = samp_avg, samp_std_dev = samp_std_dev)
  return(stats) 
  }
```

###STEP 2

write a loop that does this:

* Runs the above function 1000 times, with samp_size = 50 and samp_rate = 1/10000
* Saves all of the sample means in a vector called sample_means, and all of the sample standard deviations in a vector called `sample_sds`
```{r}
n_loops <-1000
samp_size <- 50
samp_rate <- 1/10000
sample_means <- rep(NA, n_loops)
sample_sds <- rep(NA, n_loops)
for (i in 1:n_loops) {
  resVector <- samp_fun(samp_size,samp_rate)
  sample_means[[i]]<- resVector$samp_avg
  sample_sds[[i]]<-resVector$samp_std_dev
}
```

### STEP 3

* plot your sample means as a histogram
* output the standard deviation of your sample means
* calculate the theoretical standard error (σ = 10000, n = sample size)
* calculate the mean of the sample standard deviations and use this to calculate the empirical standard
error
```{r}
tibble_means <- as.tibble(sample_means)
ggplot(tibble_means,aes(x = value))+geom_histogram()
sd(sample_means)
10000/sqrt(samp_size)
```
### STEP 4
Repeat STEP 2 and STEP 3 using a sample size of 5000.
```{r}
samp_size_big = 5000
for (i in 1:n_loops) {
  resVector <- samp_fun(samp_size_big,samp_rate)
  sample_means[[i]]<- resVector$samp_avg
  sample_sds[[i]]<-resVector$samp_std_dev
}
tibble_means <- as.tibble(sample_means)
ggplot(tibble_means,aes(x = value))+geom_histogram()
sd(sample_means)
10000/sqrt(samp_size_big)
```

