---
title: "COMPSCIX415.2-003 Session 2"
author: "ben kimel green"
date: "2/6/2019"
output: 
  html_document: 
    toc: yes
    self_contained: true
---

```{r setup, include=FALSE , warning=FALSE, message=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE,warning=FALSE, message=FALSE)
data(mpg)
```
#3.2.4 Exercises
<br />
1 <br />
Q:Run ggplot(data = mpg). What do you see?<br />
A: I see an empty graph 
```{r}
 ggplot(data = mpg)
```
<br />
2<br />
Q: How many rows are in mpg? How many columns?<br />
A: 234 rows and 11 columns
```{r}
nrow(mpg)
ncol(mpg)
```
<br />
3<br />
Q:What does the drv variable describe? Read the help for ?mpg to find out.<br />
A:The drv variable tells us if a car is front, back or 4 wheel drive 
```{r}
?mpg
```
4<br />
Make a scatterplot of hwy vs cyl.
```{r}
ggplot(data = mpg)+geom_point(mapping = aes(x = hwy,y=cyl))
```
5<br />
Q: What happens if you make a scatterplot of class vs drv? Why is the plot not useful?<br />
A:The plot is not very useful since both varaiables are qualtative and it maybe better to have the results in a table or some other visualisation method
```{r}
ggplot(data = mpg)+geom_point(mapping = aes(x = class,y=drv))
```

