---
title: "COMPSCIX 415.2 Homework 3"
author: "ben kimel green"
date: "2/14/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```
##3.8.1 Exercises
1.<br/>
Q:What is the problem with this plot? How could you improve it?<br/>
A: The points in this plot are on top of each other so it's hard to see the actual distribution. We can use jitter to solve it <br/>

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()+ggtitle("Bad Plot")
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point(position = "jitter")+ggtitle("Better Plot")
``` 
<br/>
2.<br/>
Q:What parameters to `geom_jitter()` control the amount of jittering?
A:We can control the amount of jitter passing `height` and `width` parameters. see following examples. <br/>
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()+ggtitle("override jitter by setting to 0 jitter")+geom_jitter(width = 0,height = 0)
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()+ggtitle("jitter width only")+geom_jitter(width =0.5,height = 0)
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()+ggtitle("jitter height only")+geom_jitter(width = 0,height = 0.5)
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()+ggtitle("jitter height and width")+geom_jitter(width = 0.5,height = 0.5)
```
<br/>
3.<br/>
Q: Compare and contrast `geom_jitter()` with `geom_count()`<br/>
A: `geom_count()` helps solve the same issue as `geom_jitter()` by visualizing how many observetions are at a location on the plot. The diffrence is it visualizes this by mapping the point size to the amount of observetion at a location<br/>
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()+ggtitle("Jitter")+geom_jitter()
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()+ggtitle("Count")+geom_count()
```
<br/>
4.<br/>
Q: What’s the default position adjustment for `geom_boxplot()`? Create a visualisation of the mpg dataset that demonstrates it.<br/>
A:Not sure couldn't make a diffrence using position
```{r}
ggplot(data = mpg, mapping = aes(x = class, y = hwy)) + 
  geom_boxplot()
```
##3.9.1
2.<br/>
Q: What does `labs()` do? Read the documentation.
A: `labs()` enables editing all the labels for a plot see the following example using most of `labs()` parameters
```{r}
nz <- map_data("nz")
ggplot(nz, aes(long, lat, group = group)) +
  geom_polygon(fill = "white", colour = "black") +
  coord_quickmap()+labs(title = "This is NZ",subtitle= "usually it is ommited from maps but not today",caption = "R was first created here!",x = "NZ x axis",y = "NZ y axis", tag = "a tag")
```
<br/>
4.<br/>
Q: What does the plot below tell you about the relationship between city and highway mpg? Why is `coord_fixed()` important? What does `geom_abline()` do?<br/>
A:<br/>
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +

```

