---
title: "COMPSCIX 415.2 Homework 7"
author: "ben kimel green"
date: "3/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
housesData <- read_csv("data/train.csv")
```

### Exercise 1

#### Load the train.csv dataset into R. How many observations and columns are there?

There are `r nrow(housesData)` observtions and `r ncol(housesData)` columns.


### Exercise 2

#### Visualize the distribution of SalePrice.
```{r}

ggplot(housesData)+geom_histogram(aes(SalePrice/1000),bins = 20)+xlab("Sale Price in k$")
```

####Visualize the covariation between SalePrice and Neighborhood.
```{r}
#by_hood_mean <- housesData%>%group_by(Neighborhood) %>%summarise(avg = mean(SalePrice/1000))

#ggplot(by_hood_mean,aes(x = avg,y = Neighborhood))+geom_point()+xlab("mean sale price in k$")

#by_hood_median <-housesData%>%group_by(Neighborhood) %>%summarise(med = median(SalePrice/1000))

#ggplot(by_hood_median,aes(x = med,y = Neighborhood))+geom_point()+xlab("median sale price in k$")

housesData %>% ggplot(aes(x = Neighborhood, y = SalePrice)) + geom_boxplot() +
theme_bw() +
theme(axis.text.x = element_text(angle = 90))
```

####Visualize the covariation between SalePrice and OverallQual.
```{r}
by_quality <- housesData%>%group_by(OverallQual) %>%summarise(avg = mean(SalePrice/1000))

ggplot(by_quality)+geom_point(aes(x = avg, y = OverallQual))
```

### Exercise 3

#### Our target is called `SalePrice`. First, we can fit a simple regression model consisting of only the intercept (the average of  SalePrice). Fit the model and then use the `broom` package.

I wasn't sure what is meant by fitting with the average. I used `1`. I'll ask you in class.

1. take a look at the coefficient<br/>
2. compare the coefficient to the average value of SalePrice
```{r}
    mean(housesData$SalePrice)
    (diam_lm <- lm(formula = SalePrice ~ 1, data = housesData))

```
3. take a look at the R-squared.
  (in code below)
```{r}
  tidy(diam_lm)
  glance(diam_lm)
```
## Exercise 4

#### Fit a linear regression model using `GrLivArea`, `OverallQual`, and `Neighborhood` as the features. 
```{r}
(diam_lm <- lm(formula = SalePrice ~ GrLivArea + OverallQual+ Neighborhood, data = housesData))
```

#### How would you interpret the coefficients on `GrLivArea` and `OverallQual`?

`GrLivArea` is the square fit of living space above ground. So for each square fit the price goes up by 55.56$. `OverallQual` is a scale of 1-10 for the level of finish of the house. Each grade up on this scale is about 20,951\$

#### How would you interpret the coefficient on `NeighborhoodBrkSide`?

In this model House prices in this neighborhood are 13025.45 cheaper the other. 

#### Are the features significant?

Yes, the p-value is low on most of them.

```{r}
  tidy(diam_lm)
  glance(diam_lm)
```
#### Are the features practically significant?

Yes since it makes sense to say a house will cost more money if it's bigger or has better quality of finish. it also makes sense to say that in a given neighborhood houses are cheaper or more expensive.

#### Is the model a good fit?

I think so.

## Exercise 6

####Fit a linear model to the simulated data below (use y as the target and x as the feature), and look at the resulting coefficients and R-squared. Rerun it about 5-6 times to generate different simulated datasets. What do you notice about the model’s coefficient on x and the R-squared values?

The coefficient and R-squared look like the model is very good, high r squared and low p-value. The estimate change alot and the value of R squared and the p-value .

```{r}
test_data <- function(){sim1a <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)

(diam_lm <- lm(formula = y ~ x, data = sim1a))
  
  glance(diam_lm)
  #tidy(diam_lm)
}

test_data()
test_data()
test_data()
test_data()
```